---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r readmesetup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/reconhub/rfextras/workflows/R-CMD-check/badge.svg)](https://github.com/reconhub/rfextras/actions)
[![Codecov test coverage](https://codecov.io/gh/reconhub/rfextras/branch/master/graph/badge.svg)](https://codecov.io/gh/reconhub/rfextras?branch=master)
[![R build status](https://github.com/reconhub/rfextras/workflows/R-CMD-check/badge.svg)](https://github.com/reconhub/rfextras/actions)
<!-- badges: end -->




# Welcome to *rfextras*!

*rfextras* stands for *reportfactory extras*. As its name suggests, it provides
extensions for the [{reportfactory}](https://github.com/reconhub/reportfactory),
a package providing a simple infrastructure for handling multiple *rmarkdown*
documents. Unlike the *reportfactory* which is relatively agnostic in terms of
workflows, these extensions tend to implement more opinionated tools, which may
be useful only for some users.


## Installing the package

To install the development version of the package, use:

```{r install2, eval = FALSE}
remotes::install_github("reconhub/rfextras")
```


## Overview

{rfextras} provides several features, broken down in functions meant to be used
within reports, or outside.

### Features to be used inside reports

Here is a quick list of features provided by {rfextras}, to be used inside
`.Rmd` documents.

* `load_scripts()`: safely loads all `.R` files in a given folder (defaulting to
  `scripts/`)

* `find_latest()`: find the latest version of a file, when several dated versions
  exist (e.g. find the latest dataset)





## Contributing guidelines

Contributions are welcome via **pull requests**.


### Code of Conduct

Please note that the reportfactory project is released with a 
[Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

